forrechelle

### 2020-01-22 analysis/20_forrechelle.Rmd
new colors

candidategenes <- c("PRLR", "PRL", "CISH", "JAK2", "SOCS3", "GH" )
datadrivengenes <- c("COX1", "PRL", "CHGA", "ATP2B4", "LOC107055658")
timepoints <- charlevels

@@

df <- datapathfile %>%
  setNames(nm = .) %>%
  map_df(~read_csv(.x, col_types = cols(), col_names = T), .id = "filename") %>% 
  mutate(tissue = sapply(strsplit(as.character(filename),'../results/06_'), "[", 2)) %>% 
  mutate(tissue = sapply(strsplit(as.character(tissue),'allvsd.csv'), "[", 1))  %>% 
  select(tissue, X1, everything()) 
```

@@

write.csv(tissuespecificity, "../results/tissuespecificity.csv")

genes <- as.data.frame(df$X1)

df2 <-  df  %>%
  filter(X1 %in% candidategenes) %>%
  pivot_longer(cols = L.Blu13_male_gonad_control.NYNO:y98.o50.x_male_pituitary_inc.d3, 
               names_to = "sample", values_to = "vsd") %>%
   mutate(sex = sapply(strsplit(as.character(sample),'_'), "[", 2)) %>%
   mutate(treatment = sapply(strsplit(as.character(sample),'_'), "[", 4))  %>%
   mutate(treatment = sapply(strsplit(as.character(treatment),'.NYNO'), "[", 1)) %>%
  mutate(bird = sapply(strsplit(as.character(sample),'_'), "[", 1)) %>%
  filter(treatment %in% timepoints) %>%
  select(bird, sex, treatment, tissue, X1, vsd) %>%
  mutate(tissue = fct_recode(tissue, "hypothalamus" = "hyp",
                    "pituitary" = "pit",
                    "gonads" = "gon"
                    )) %>%
  rename(gene = X1) %>%
  drop_na() %>%
  droplevels()
head(df2)

df2$treatment <- factor(df2$treatment, levels = alllevels)
df2$tissue <- factor(df2$tissue, levels = tissuelevels)

df4 <-  df  %>%
  dplyr::filter(X1 %in% datadrivengenes) %>%
  pivot_longer(cols = L.Blu13_male_gonad_control.NYNO:y98.o50.x_male_pituitary_inc.d3, 
               names_to = "sample", values_to = "vsd") %>%
   mutate(sex = sapply(strsplit(as.character(sample),'_'), "[", 2)) %>%
   mutate(treatment = sapply(strsplit(as.character(sample),'_'), "[", 4))  %>%
   mutate(treatment = sapply(strsplit(as.character(treatment),'.NYNO'), "[", 1)) %>%
  mutate(bird = sapply(strsplit(as.character(sample),'_'), "[", 1)) %>%
  dplyr::filter(treatment %in% timepoints) %>%
  dplyr::select(bird, sex, treatment, tissue, X1, vsd) %>%
  mutate(tissue = fct_recode(tissue, "hypothalamus" = "hyp",
                    "pituitary" = "pit",
                    "gonads" = "gon"
                    )) %>%
  rename(gene = X1) %>%
  drop_na() %>%
  droplevels()
head(df4)

@@

df2$gene <- factor(df2$gene)

dft <- df %>% filter(X1 %in% candidategenes) %>%
  unite("tissuegene", tissue:X1, remove = FALSE) %>%
  select(-tissue, -`X1`, -filename)  %>%
  pivot_longer(-tissuegene, names_to = "samples", values_to = "vsd") %>%
  drop_na() %>%
  mutate("bird" = sapply(strsplit(as.character(samples),'\\_'), "[", 1)) %>%
  select(bird,tissuegene,vsd) %>%
  filter(bird != "x.g.g.ATLAS") %>%
  pivot_wider(id_cols = bird, names_from = tissuegene, values_from = vsd)
dft <- as.data.frame(dft)
row.names(dft) <- dft$bird
dft$bird <- NULL
head(dft)
```

@@

```{r victoria-ePRL-corr}
x <- correlate(dft)

>>>>

candidategenes <- c("PRLR", "PRL", "CISH", "JAK2", "SOCS3", "GH" )
datadrivengenes <- c("COX1", "PRL", "CHGA", "ATP2B4", "LOC107055658")

calisigenes <- c("PRL", "PRLR", 
                 "VIP", "VIPR1", "VIPR2", 
                 "OXT", "AVP", "AVPR1A", "AVPR1B", 
                 "GNRH1","GNRHR", "NPVF",
                 "NR3C1", "NR3C2",
                 "ESR1", "ESR2", "AR")

timepoints <- charlevels

@@

df <- datapathfile %>%
  setNames(nm = .) %>%
  map_df(~read_csv(.x, col_types = cols(), col_names = T), .id = "filename") %>% 
  mutate(tissue = sapply(strsplit(as.character(filename),'../results/06_'), "[", 2)) %>% 
  mutate(tissue = sapply(strsplit(as.character(tissue),'allvsd.csv'), "[", 1))  %>% 
  select(tissue, X1, everything())

genes <- as.data.frame(df$X1)
```
## tissue specificiity

@@

write.csv(tissuespecificity, "../results/tissuespecificity.csv")
```

## candidate genes

```{r candidates}

df2 <-  df  %>%
  filter(X1 %in% c(candidategenes)) %>%
  pivot_longer(cols = L.Blu13_male_gonad_control.NYNO:y98.o50.x_male_pituitary_inc.d3, 
               names_to = "sample", values_to = "vsd") %>%
   mutate(sex = sapply(strsplit(as.character(sample),'_'), "[", 2)) %>%
   mutate(treatment = sapply(strsplit(as.character(sample),'_'), "[", 4))  %>%
   mutate(treatment = sapply(strsplit(as.character(treatment),'.NYNO'), "[", 1)) %>%
  mutate(bird = sapply(strsplit(as.character(sample),'_'), "[", 1)) %>%
  filter(treatment %in% timepoints) %>%
  select(bird, sex, treatment, tissue, X1, vsd) %>%
  mutate(tissue = fct_recode(tissue, "hypothalamus" = "hyp",
                    "pituitary" = "pit",
                    "gonads" = "gon"
                    )) %>%
  rename(gene = X1) %>%
  drop_na() %>%
  droplevels()
head(df2)

df2$treatment <- factor(df2$treatment, levels = alllevels)
df2$tissue <- factor(df2$tissue, levels = tissuelevels)
df2$gene <- factor(df2$gene)

@@

@@

```{r victoria-ePRL-corr}

dft <- df %>% filter(X1 %in% candidategenes) %>%
  unite("tissuegene", tissue:X1, remove = FALSE) %>%
  select(-tissue, -`X1`, -filename)  %>%
  pivot_longer(-tissuegene, names_to = "samples", values_to = "vsd") %>%
  drop_na() %>%
  mutate("bird" = sapply(strsplit(as.character(samples),'\\_'), "[", 1)) %>%
  select(bird,tissuegene,vsd) %>%
  filter(bird != "x.g.g.ATLAS") %>%
  pivot_wider(id_cols = bird, names_from = tissuegene, values_from = vsd)
dft <- as.data.frame(dft)
row.names(dft) <- dft$bird
dft$bird <- NULL
head(dft)

x <- correlate(dft)
